ES Models: Random Forest

### 2025-03-11 randomforest_kl.Qmd
add random forest

    # if(file.exists("RandomForest/ES-RF.RDA")) load("ES-RF.RDA")

@@

    with(wfs, plot(pollinators_base, delta_pollinators.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Pollination"))

    with(wfs, plot(ann_agr_pland, delta_pollinators.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Pollination"))

@@

    with(wfs, plot(n_export_base, delta_n_export.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Nitrogen"))

    with(wfs, plot(ann_agr_pland, delta_n_export.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Nitrogen"))

@@

    with(wfs, plot(sed_export_base, delta_sed.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Sediment"))

    with(wfs, plot(ann_agr_pland, delta_sed.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Sediment"))

@@

    with(wfs, plot(qb_base, delta_qb.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Baseflow"))

    with(wfs, plot(ann_agr_pland, delta_qb.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Baseflow"))

@@

    if(!exists("pollinators_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_pollinators.margin, orig = wfs$pollinators_base, dat.predictors)
        pollinators_base.ann_agr_pland.pdp <- partial(pollinators_base.rf, train = dat, pred.var = "ann_agr_pland")
        pollinators_margin.ann_agr_pland.pdp <- partial(pollinators_margin.rf, train = dat, pred.var = "ann_agr_pland")
        pollinators_base.ntr_pland.pdp <- partial(pollinators_base.rf, train = dat, pred.var = "ntr_pland")
        pollinators_margin.ntr_pland.pdp <- partial(pollinators_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("n_export_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_n_export.margin, orig = wfs$n_export_base, dat.predictors)
        n_export_base.ann_agr_pland.pdp <- partial(n_export_base.rf, train = dat, pred.var = "ann_agr_pland")
        n_export_margin.ann_agr_pland.pdp <- partial(n_export_margin.rf, train = dat, pred.var = "ann_agr_pland")
        n_export_base.ntr_pland.pdp <- partial(n_export_base.rf, train = dat, pred.var = "ntr_pland")
        n_export_margin.ntr_pland.pdp <- partial(n_export_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("sed_export_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_sed.margin, orig = wfs$sed_export_base, dat.predictors)
        sed_export_base.ann_agr_pland.pdp <- partial(sed_export_base.rf, train = dat, pred.var = "ann_agr_pland")
        sed_export_margin.ann_agr_pland.pdp <- partial(sed_export_margin.rf, train = dat, pred.var = "ann_agr_pland")
        sed_export_base.ntr_pland.pdp <- partial(sed_export_base.rf, train = dat, pred.var = "ntr_pland")
        sed_export_margin.ntr_pland.pdp <- partial(sed_export_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("qb_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_qb.margin, orig = wfs$qb_base, dat.predictors)
        qb_base.ann_agr_pland.pdp <- partial(qb_base.rf, train = dat, pred.var = "ann_agr_pland")
        qb_margin.ann_agr_pland.pdp <- partial(qb_margin.rf, train = dat, pred.var = "ann_agr_pland")
        qb_base.ntr_pland.pdp <- partial(qb_base.rf, train = dat, pred.var = "ntr_pland")
        qb_margin.ntr_pland.pdp <- partial(qb_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

>>>>

    if(file.exists("data/ES-RF.RDA")) load("data/ES-RF.RDA")

@@

    with(wfs, plot(pollinators_base, delta_pollinators_max.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Pollination"))

    with(wfs, plot(ann_agr_pland, delta_pollinators_max.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Pollination"))

@@

    with(wfs, plot(n_export_base, delta_n_export_max.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Nitrogen"))

    with(wfs, plot(ann_agr_pland, delta_n_export_max.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Nitrogen"))

@@

    with(wfs, plot(sed_export_base, delta_sed_max.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Sediment"))

    with(wfs, plot(ann_agr_pland, delta_sed_max.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Sediment"))

@@

    with(wfs, plot(qb_base, delta_qb_max.margin, col = "darkgreen", xlab = "Base value", ylab = "Delta", main = "Baseflow"))

    with(wfs, plot(ann_agr_pland, delta_qb_max.margin, col = "purple", xlab = "Annual agriculture (%)", ylab = "Delta", main = "Baseflow"))

@@

    if(!exists("pollinators_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_pollinators_max.margin, orig = wfs$pollinators_base, dat.predictors)
        pollinators_base.ann_agr_pland.pdp <- partial(pollinators_base.rf, train = dat, pred.var = "ann_agr_pland")
        pollinators_margin.ann_agr_pland.pdp <- partial(pollinators_margin.rf, train = dat, pred.var = "ann_agr_pland")
        pollinators_base.ntr_pland.pdp <- partial(pollinators_base.rf, train = dat, pred.var = "ntr_pland")
        pollinators_margin.ntr_pland.pdp <- partial(pollinators_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("n_export_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_n_export_max.margin, orig = wfs$n_export_base, dat.predictors)
        n_export_base.ann_agr_pland.pdp <- partial(n_export_base.rf, train = dat, pred.var = "ann_agr_pland")
        n_export_margin.ann_agr_pland.pdp <- partial(n_export_margin.rf, train = dat, pred.var = "ann_agr_pland")
        n_export_base.ntr_pland.pdp <- partial(n_export_base.rf, train = dat, pred.var = "ntr_pland")
        n_export_margin.ntr_pland.pdp <- partial(n_export_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("sed_export_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_sed_max.margin, orig = wfs$sed_export_base, dat.predictors)
        sed_export_base.ann_agr_pland.pdp <- partial(sed_export_base.rf, train = dat, pred.var = "ann_agr_pland")
        sed_export_margin.ann_agr_pland.pdp <- partial(sed_export_margin.rf, train = dat, pred.var = "ann_agr_pland")
        sed_export_base.ntr_pland.pdp <- partial(sed_export_base.rf, train = dat, pred.var = "ntr_pland")
        sed_export_margin.ntr_pland.pdp <- partial(sed_export_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }

    if(!exists("qb_base.ann_agr_pland.pdp")) {
        dat <- data.frame(y = wfs$delta_qb_max.margin, orig = wfs$qb_base, dat.predictors)
        qb_base.ann_agr_pland.pdp <- partial(qb_base.rf, train = dat, pred.var = "ann_agr_pland")
        qb_margin.ann_agr_pland.pdp <- partial(qb_margin.rf, train = dat, pred.var = "ann_agr_pland")
        qb_base.ntr_pland.pdp <- partial(qb_base.rf, train = dat, pred.var = "ntr_pland")
        qb_margin.ntr_pland.pdp <- partial(qb_margin.rf, train = dat, pred.var = "ntr_pland")
        rm(dat)
    }
